Simulating NHST and TOST

### 2017-10-14 NHST_and_TOST.Rmd
update simulation (N = 80% power given equivalence bounds, p-dist plot).

```{r}
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
#Simulating one-sample t-tests

```{r}
require(TOSTER)
n <- 100 #set sample size
low_eqbound=-0.3
high_eqbound=0.3
sd_true<-1
m_true<-0.3
mu<-0.3
alpha<-0.05
nSims <- 1000000 #number of simulated experiments
pttest<-numeric(nSims) #set up empty container for all simulated p-values
ptost<-numeric(nSims) #set up empty container for all simulated p-values
tlist<-numeric(nSims) #set up empty container for all simulated p-values
p1list<-numeric(nSims) #set up empty container for all simulated p-values
p2list<-numeric(nSims) #set up empty container for all simulated p-values
LLlist<-numeric(nSims)
ULlist<-numeric(nSims)

@@

p<-data.frame(ptost,pttest)
plot(ptost,pttest)

>>>>

```{r}
options(scipen=999)
library(knitr)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
```
#Simulating one-sample t-tests

```{r}
require(TOSTER)
n <- 50 #set sample size
low_eqbound=-0.3
high_eqbound=0.3
sd_true<-1
m_true<-0.0
mu<-0.0
alpha<-0.05

require("TOSTER")
n<-powerTOSTone(alpha=alpha, statistical_power=0.8, low_eqbound_d=-low_eqbound, high_eqbound=0.3)
n<-ceiling(n)

nSims <- 1000000 #number of simulated experiments
pttest<-numeric(nSims) #set up empty container for all simulated p-values
ptost<-numeric(nSims) #set up empty container for all simulated p-values
tlist<-numeric(nSims) #set up empty container for all simulated p-values
p1list<-numeric(nSims) #set up empty container for all simulated p-values
p2list<-numeric(nSims) #set up empty container for all simulated p-values
LLlist<-numeric(nSims)
ULlist<-numeric(nSims)

@@

p<-data.frame(ptost,pttest)
#look only at significant TOST results
p_sig_TOST<-p[which(ptost<alpha),]
#Plot the p-values for the NHST t-test, but only those for significant TOT results. 
hist(p_sig_TOST$pttest, breaks=100)

#How often is a test significant AND equivalent?
nrow(p[which(ptost<alpha & pttest<alpha),])/nSims

#plot p-values against each other for TOST and NHST
plot(ptost,pttest)
